---
title: "Assignment3 StringR"
author: "Randall Thompson"
date: "9/15/2019"
output:
  html_document:
    df_print: paged
---
```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:].,, ]{2,}"))
```
## Problem 3
Rearrange vector as first name last name
```{r}
nameFirstLast <- sapply(strsplit(name, ", "),function(x){paste(rev(x),collapse=" ")})
print(nameFirstLast)
```
Logic vector whether a character has a title
```{r}
str_detect(name, c("Dr.|Rev.")) 
```
Logic vector whether a character has a second name (abbreviated first name)
```{r}
str_detect(name, "[A-Z][.]")
```

## Problem 4
#### a 
#[0-9]+\\$ 
Any number between 0-9, 1 or more times at the end of a line. 

111

#### b 
#\\b[a-z]{1,4}\\b
A word starts with any lowercase letter a-z and is between 1-4 letters long.

cat

#### c 
#.*?\\.txt$
Any character followed by ".txt" at the end of the line. This is a lazy format so the program stops at the first ".txt".

blah.txt

#### d
#\\d{2}/\\d{2}/\\d{4}
Two digits 0-9, a forward slash, two digits 0-9, a forward slash, then four digits 0-9

09/15/2019

#### e 
#<(.+?)>.+?</\\1>
Opening tag with any character in lazy format, any character in lazy format, closing tag matching the opening tag.

#<title>This is the title</title>